CUNY SPSS Data Science Math Homework 1

### 2018-07-20 data-science-math/Homework 1.Rmd
More work on HW 1

```{r setup, include=FALSE}
library(Deriv)
knitr::opts_chunk$set(echo = TRUE)
```

@@

$$C(x,y) = 3(4xy) + 3x^2 + 5x^2 = 12xy+8x^2$$
Substituting in y:
$$ C(x)=\frac{12x\cdot 18432}{x^2}+8x^2=\frac{221184}{x}+8x^2$$
Minimize the cost function:
$$ C'(x)=-\frac{221184}{x^2}+16x$$
$$ 0=-\frac{221184}{x^2}+16x\Rightarrow 0=-221184+16x^3 \Rightarrow 0=-13824 + x^3 $$
$$ x^3 = 13824 \Rightarrow x=\sqrt[3]{13824} = 24$$
Plugging 24 into the volume equation and solving for y:
$$18432 = x^2y\Rightarrow 18432=(24)^2 y\Rightarrow 18432=576 y \Rightarrow y=\frac{18432}{576} \Rightarrow y = 32$$
Now checking everything with R:
```{r}
f22 <- function(x){
  (3*(4*x*(18432/(x**2)))) + (3*x**2) + (5*x**2)
}
f22_prime <- Deriv(f22)
library(rootSolve)
x22 <- uniroot.all(f22_prime, c(0,100))
x22
y22 <- function(x){18432/(x**2)}
y22(x22)
```

@@

@@

@@

@@

### Question 26

@@

### Question 27

@@

### Question 28

@@

******
### Question 30

@@

f30(-7,2)
```
******

@@

@@

>>>>

```{r setup, include=FALSE}
library(Deriv)
library(rootSolve)
knitr::opts_chunk$set(echo = TRUE)
```

@@

$$C(x,y) = 3(4xy) + 3x^2 + 5x^2 = 12xy+8x^2$$
Substituting in y:
$$ C(x)=\frac{12x\cdot 18432}{x^2}+8x^2=\frac{221184}{x}+8x^2$$
Minimize the cost function:
$$ C'(x)=-\frac{221184}{x^2}+16x$$
$$ 0=-\frac{221184}{x^2}+16x\Rightarrow 0=-221184+16x^3 \Rightarrow 0=-13824 + x^3 $$
$$ x^3 = 13824 \Rightarrow x=\sqrt[3]{13824} = 24$$
Plugging 24 into the volume equation and solving for y:
$$18432 = x^2y\Rightarrow 18432=(24)^2 y\Rightarrow 18432=576 y \Rightarrow y=\frac{18432}{576} \Rightarrow y = 32$$
Now checking everything with R:
```{r}
f22 <- function(x){
  (3*(4*x*(18432/(x**2)))) + (3*x**2) + (5*x**2)
}
f22_prime <- Deriv(f22)

x22 <- uniroot.all(f22_prime, c(0,100))
x22
y22 <- function(x){18432/(x**2)}
y22(x22)
```

@@

$$Area=xy=1056 \Rightarrow y=\frac{1056}{x}$$

The cost function is

$$C(x,y)=(14.40\cdot 2y)+(14.40 \cdot 2x) + (12.00 \cdot 2x)$$
Substituting y in:
$$C(x)=(14.40\cdot 2(\frac{1056}{x}))+(14.40 \cdot 2x) + (12.00 \cdot 2x)$$
Simplified
$$C(x)=\frac{30412.8}{x}+52.8x$$

Minimize it

$$C'(x)=-\frac{30412.8}{x^2}+52.8$$

$$0=-\frac{30412.8}{x^2}+52.8 $$
$$\frac{30412.8}{x^2}=52.8 $$
$$ \frac{30412.8}{52.8}=x^2 $$
$$x^2=576 $$
$$ x=\sqrt{576} \Rightarrow x=\pm 24$$
Negative 24 is meaningless in this context.  Now substituting x in the area equation:
$$y=\frac{1056}{24} = 44$$

```{r}
f23 <- function(x){
  (28.8*(1056/x))+(52.8*x)
}
f23_prime <- Deriv(f23)

x23 <- uniroot.all(f23_prime, c(0,100))
x23
y23 <- function(x){1056/x}
y23(x23)
```

@@

$$Value(time)=base \cdot e^{rate \cdot time}$$
Enter in the information from the question:

$$37000=67000 \cdot e^{rate \cdot 7}$$

Solving for rate:

$$\frac{37000}{67000} = e^{rate \cdot 7}$$

$$ln\Big(\frac{37000}{67000}\Big) = rate \cdot 7 \Rightarrow rate = \frac{ln\Big(\frac{37000}{67000}\Big)}{7} \approx -0.08482496$$

Now substitue and solve for the value at year 9

$$Value(9) = 67000 \cdot e^{-0.08482496 \cdot (9)} = 31226.53$$
Checking my math with R:
```{r}
f24 <- function(t){
  e <- exp(1)
  67000*e**(t*((log(37000/67000)/7)))
}
f24(9)
```

@@

Given $p = D(x) = 23.2-0.4x$ price and Revenue is $R = p \cdot D(x)$ the maximizing level of production is:

$$ R = p \cdot D(x) \Rightarrow R(x) = D(x) \cdot D(x) \Rightarrow R(x) = D(x)^2$$

Using the chain rule:
$$R'(x) = 0.32x -18.56$$

$$0 = 0.32x -18.56 \Rightarrow 0.32x = 18.56 \Rightarrow x = \frac{18.56}{0.32} = 58$$

Checking the math in R:
```{r}
f25 <- function(x){
  (23.2-0.4*x)*(23.2-0.4*x)
}

f25_prime <- Deriv(f25)
x25 <- uniroot.all(f25_prime, c(0,100))
x25
```

@@

### Question 26
Start with the exponential growth formula:
$$Cost(time)=base \cdot e^{rate \cdot time}$$

And enter what we know and solve for rate:
$$426.8=400 \cdot e^{rate \cdot 11} \Rightarrow \frac{426.80}{400}=e^{rate \cdot 11} \Rightarrow rate\cdot 11 = ln\Big(\frac{426.8}{400}\Big) \Rightarrow rate = \frac{ln\Big(\frac{426.8}{400}\Big)}{11} \approx 0.005895543$$

Substitute rate back into the equation:
$$Cost(year) = 400 \cdot e^{0.005895543 \cdot (year - 1995)}$$
$$Cost(2017) = 400 \cdot e^{0.005895543 \cdot (2017 - 1995)} \approx 455.40$$
Verifying with R:
```{r}
f26 <- function(year){
  e <- exp(1)
  400*e**((log(426.8/400)/11)*(year-1995))
}
f26(2017)
```

@@

### Question 27
Given:
$$P'(x) = 380-4x $$
$$P(x) = 380x - 2x^2+C$$

$$1700 = 380(38)-2(38)^2 + C$$
Solving for C

$$ 1700 = 14440 - 2888 + C \Rightarrow C = 17000 - 14440 + 2888 \Rightarrow C = -9852$$
The profit function is:
$$ P(x)= 380x - 2x^2-9852$$

#### Step 4
$$ P(56)= 380(56) - 2x^2-9852 = 5156$$
```{r}
f27 <- function(x){
  (380*x) - (2*x**2) - 9852
}
f27(56)
```

@@

### Question 28
Solve:
$$ \int\frac{-5(ln(y))^3}{y}dy = -5 \int \frac{1}{y} ln(y)^3$$
Substitute
$u = ln(y)$ and $du = \frac{1}{y}$

$$-5 \int du \cdot u^3 \Rightarrow -5 \cdot \frac{u^4}{4}+c \Rightarrow \frac{-5}{4}ln(y)^4 + c$$

@@

Given:
$$P'(t)=75-9t^\frac{1}{2}$$

$$P(t) = 75t-6t^\frac{3}{2}$$

$$\int_0^9 P'(t) = P(9) - P(0) = (75(9)-6(9)^\frac{3}{2})-(0-0) = (675-162) -0 = 513$$

### Question 30

@@

f30(-7,2)
```

@@

### Question 32

Checking my math with R:
```{r}
f32 <- function(x){x*((x+7)**(1/2))}
integrate(Vectorize(f32),-7, 2)
```

@@

I currently don't know how to do find the Taylor polnomial of degree 5 near x=4 for $y=3e^{5x-3}$
